---
title: "1. Statsbomb_Data_Import"
author: "Stone_J"
format: html
editor: visual
---

## Statsbomb Data Import

Please note you need to have installed the StatsbombR package prior to using this code. Info can be found here: https://statsbomb.com/wp-content/uploads/2021/11/Working-with-R.pdf

## Importing Data

First we load the packages needed for the code tidyverse laods many differnert packages, for this code it inculde dplyr and magrittr StatsBombR loads StatsBombR

```{r}
#load packages 
library(tidyverse)
library(StatsBombR)
```

\*\*\*Loading Statsbomb Data into R Studio\*\*\*

This loads the free competitions data and shows which data is available. See the document "Free Data Competition ID" which shows what the Competition ID and Season ID refer to.

```{r}
df_comp <- FreeCompetitions() # df = dataframe
df_comp
```

Here, we select the women world cup from 2023 as our data set. We define the dataframe as df_world_cup. We also import the matches from the competition (df_matches) and the event data (df_events).

```{r}
df_world_cup <- FreeCompetitions() %>% 
  filter(competition_id==72 & season_id==107) #use the Comp df to get the id vaules
df_matches <- FreeMatches(df_world_cup)
df_events <- free_allevents(MatchesDF = df_matches, Parallel = T) #this imports the event data
```

```{r}
#this uses a statsbomb function to clean the data and creates some useful extra columns. 
df_events <- StatsBombR::allclean(StatsBombEvents)
```

You are now ready to move to 2. Working with Data.

## Importing 360 Data

```{r}
comp <- FreeCompetitions() %>% 
  filter(competition_id==72 & season_id==107) #women world cup 23
matches <- FreeMatches(comp)
df360 <- free_allevents_360(MatchesDF = matches, Parallel = T)
```

```{r}
#load events data 
df <- free_allevents(MatchesDF = matches, Parallel = T)
df <- allclean(df)
df <- get.opposingteam(df)
```

```{r}
df360 = df360 %>% rename(id = event_uuid)
df = df %>% left_join(df360, by = c("id" = "id"))
df = df %>% rename(match_id = match_id.x) %>% select(-match_id.y)
```

## Clean the df and adding columns of data for analysis
